Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

To validate the effectiveness of our proposed defense, we conduct experiments
on three commonly used DML datasets: CUB-200-2011 (CUB)~\cite{cub200}, Cars-196
(CARS)~\cite{cars196}, and Stanford-Online-Products (SOP)~\cite{sop}.
%
We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
for ease of comparison.
%
The setup is also consistent to standard DML~\cite{revisiting}.

Specifically, we train a ResNet-18 (RN18)~\cite{resnet} with the output dimension of
the last layer changed to $N=512$.
%
The margin $\gamma$ in triplet loss is set as $0.2$ by default.
%
The model is trained with Adam optimizer with learning rate $1.0\times 10^{-3}$
for $150$ epochs, with mini-batch size set as $112$.

For adversarial training, we adopt the perturbation budget of
$\varepsilon=8/255$ in infinity norm ($p=\infty$).
%
Projected Gradient Descent (PGD)~\cite{madry} is used for creating adversarial
examples, with a maximum step number set as $\eta=8$ by default.\footnote{
Instead of $\eta=32$ as in \cite{robrank} in order to control time consumption.}
%
Step size for PGD is set as $\alpha=1/255$.

>>>>

% evaluation: dataset

To validate the proposed defense, we conduct experiments
on three commonly used DML datasets: CUB-200-2011 (CUB)~\cite{cub200}, Cars-196
(CARS)~\cite{cars196}, and Stanford-Online-Products (SOP)~\cite{sop}.
%
We follow the same experiment setup as the state-of-the-art work~\cite{robrank}
for ease of comparison.

% evaluation: configuration

Specifically, we (adversarially) train imagenet-initialized ResNet-18
(RN18)~\cite{resnet} with the output dimension of the last layer changed to
$N=512$.
%
The margin $\gamma$ in triplet loss is $0.2$ by default.
%
Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
as $1.0\times 10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.

For adversarial training, we adopt the perturbation budget of
$\varepsilon=8/255$ in infinity norm ($p=\infty$).
%
Projected Gradient Descent (PGD)~\cite{madry} is used for creating adversarial
examples, with a maximum step number set as $\eta=8$ by default.\footnote{
Instead of $\eta=32$ as in \cite{robrank} in order to control time consumption.}
%
Step size for PGD is set as $\alpha=1/255$.
%
The setup is also consistent to standard DML~\cite{revisiting}.
